Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-03-17 paper.tex
update

Existing works on service composition focus mainly on addressing one of challenges above. Many works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as a \textit{semi-automated Web service composition} approach \cite{parejo2008qos,bahadori2009optimal}. Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, with the hope of eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{boustil2014semantic, mier2015integrated, bansal2016generalized}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously and achieved a desired balance.

The overall goal of this paper is to \textit{develop an general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality model. We will achieve three objectives in this work as follows:

@@

\section{Related Work} \label{relatedWork}
Substantial work on web service composition focused on either semantic web service composiiton \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic mathmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.

@@

A heuristic service composition method is proposed by Qi et al. \cite{qi2010combining} for QoS-aware web service composiiton, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS. Obviously, there exists scalability problem for enumeration techniques.

Evolutionary Computation (EC) techniques are used to improve the scalability for solving NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm to the problem of QoS-ware web service composition, and a set of binary strings are used as individuals, which demands to be decoded into composition solutions. Genetic Programming are employed by  \cite{yu2013adaptive} with direct representation of composition solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions. A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to generate directed acrylic graph as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques. To eliminating the transformation process from DAG, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as indirect representation as composition solution that decoding into Direct Acyclic Graph (DAG). These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

@@

In summary, composition solutions from semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} does not consider QoS, and QoS-aware web service composiiton \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function. Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}. In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability. Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps discussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performance by comparing with one existing GP-based approach.

@@

\begin{itemize}
\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ O_{S_1} \in S_{1} \equiv I_{S_2} \in S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S_1} \in S_{1} \sqsubseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S_1} \in S_{1} \sqsupseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
\item \textit{Fail} ($\perp$). Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($O_{S_1} \in S_{1} \perp I_{S_2} \in S_{2}$), if none of the previous matches discovered.
\end{itemize}

@@

\subsection{Objective Function}
In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions. It is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation8}). Note that weights can be adjusted according to users' preferences. The function value of 1 means the best comprehensive quality and 0 means the worst. For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1. Therefore, the service composition is try to maximise the value of objective function.
\vspace{-0.2cm}
\begin{equation}
\label{equation8}
Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\
\vspace{-0.2cm}
\begin{equation}
\label{equation9}
\hat{Q_k} = 
\begin{cases}
	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if }Q_{k, max} - Q_{k, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ is $MT$, $Q_2$ is $S$, $Q_3$ is $A$, and $Q_4$ is $R$.
\begin{equation}
\label{equation10}
\hat{Q_j} = 
\begin{cases}
	\frac{Q_{j,max} - Q_j}{Q_{j, max} - Q_{j, min}} & \text{ if }Q_{j, max} - Q_{j, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ is $T$ and $Q_2$ is $C$.

\section{PSO-based Approach to QoS-Aware Semantic Web Service Composition}\label{qswsc_approach}

@@

PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both semantic matchmaking quality and QoS. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 4. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation with explicit support for the proposed quality model.

\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic web service matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality. The key idea of the index is to create a map using a pair of keys, output-related concepts and potentially matched input-related concepts with considering different levels of match types, and the map values stored $mt_{p}$ and $mt_{s}$. Meanwhile, this index size could also be reduced by only considering the concepts related in the shrunken service repository, which means the index cache is filtered by those task-relevant web services. This optimised cache also contributes to less and constant time for weighted graphs building through the whole evolutionary process.

@@

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; and $(2)$ compare solutions generated by QoS-ware approach with our method; and $(3)$ compare our method with one existing GP-based approach.

@@

We run the experiment on computing grid comprising of 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations. We run 30 times independently for each dataset. We configure weight of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly. The $mt_{p}$ is set to 1 (Exact match) and 0.75 (Plugin). In general, weight settings and parameter match type quality are decided by users' preferences.

@@

\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO method. We consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation. Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using the proposed comprehensive quality model. To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times), we set the parameters settings for GP-based approach \cite{ma2015hybrid} using 30 individuals and 100 generations.

>>>>

Existing works on service composition focus mainly on addressing one of challenges above. Many works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as a \textit{semi-automated Web service composition} approach \cite{parejo2008qos,bahadori2009optimal}. Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, which supplements well defined semantic descriptions from the concept of ontologies, instead of parameters value. In the past few years, substantial works have been done on semantic web service composition \cite{boustil2014semantic, mier2015integrated, bansal2016generalized}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously and achieved a desired balance.

The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality model. We will achieve three objectives in this work as follows:

@@

\section{Related Work} \label{relatedWork}
Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.

@@

A heuristic service composition method is proposed by Qi et al. \cite{qi2010combining} for QoS-aware web service composition, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near-to-optimal for QoS. Obviously, there exists scalability problem for enumeration techniques.

Evolutionary Computation (EC) techniques are used to improve the scalability for solving NP-hard problems. Gupta et al. \cite{gupta2015optimization} employ an Genetic Algorithm to the problem of QoS-ware web service composition, and a set of binary strings are used as individuals, which demands to be decoded into composition solutions. Genetic Programming are employed by  \cite{yu2013adaptive} with direct representation of composition solutions, the overall quality of solutions are measured by a fitness function that is liable for penalising infeasible solutions. A hyper approach employs both a greedy search algorithm and Genetic Programming (GP) is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to generate  directed acyclic graphs (DAGs) as composition solutions, which is further transferred to the tree structure for initialisation and mutation using unfolding techniques. To eliminating the transformation process from DAGs, A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of DAGs employing Graph-based evolutionary operators like crossover and mutation. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}, an indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG as a composition solution. These QoS-aware approaches does not consider semantic matchmaking quality, which could lead to over-general outputs to be produced by selected services, The finding is evidently supported by our first comparison experiment. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS.

@@

In summary, composition solutions from semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} does not consider QoS, and QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function. Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}. In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability. Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps discussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performance by comparing with one existing GP-based approach.

@@

\begin{itemize}
\item \textit{Exact} ($\equiv$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Exact match ($ O_{S_1} \in S_{1} \equiv I_{S_2} \in S_{2}$), if  Concept $C_{2}$ and Concept $C_{3}$ are equivalent.
\item \textit{Plugin} ($\sqsubseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Plugin match ($O_{S_1} \in S_{1} \sqsubseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a sub-concept of Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of children concepts ($n=1$ stands for direct children).
\item \textit{Subsume} ($\sqsupseteq_{n}$): Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are Subsume matched($O_{S_1} \in S_{1} \sqsupseteq_{n} I_{S_2} \in S_{2}$), if  Concept $C_{2}$ is a super-concept of  Concept $C_{3}$, and $n = \{1,2,...,n \}$ presents the levels of parent concepts ($n=1$ stands for direct parent).
\item \textit{Fail} ($\perp$). Output of Web service $S_{1}$ and Input of Web service $S_{2}$ are not matched (Fail) ($O_{S_1} \in S_{1} \perp I_{S_2} \in S_{2}$), if none of the previous matches discovered.
\end{itemize}

@@

\subsection{Objective Function}
In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions. It is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation8}). Note that weights can be adjusted according to users' preferences. The function value of 1 means the best comprehensive quality and 0 means the worst. For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1 using Formula (\ref{equation9}) and (\ref{equation10}), where the maximum and minimum value of $A$, $R$, $T$, and $C$ are calculated by all web services related to the composition task. $MT$ and $S$ are using a bound from 0 to 1. Therefore, the composition task is try to find maximised value of objective function associated to the solutions.

\vspace{-0.2cm}
\begin{equation}
\label{equation8}
Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\
\vspace{-0.2cm}
\begin{equation}
\label{equation9}
\hat{Q_k} = 
\begin{cases}
	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if }Q_{k, max} - Q_{k, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ is $MT$, $Q_2$ is $S$, $Q_3$ is $A$, and $Q_4$ is $R$.
\begin{equation}
\label{equation10}
\hat{Q_j} = 
\begin{cases}
	\frac{Q_{j,max} - Q_j}{Q_{j, max} - Q_{j, min}} & \text{ if }Q_{j, max} - Q_{j, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ is $T$ and $Q_2$ is $C$.

\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}

@@

PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be easier to maintain the correctness of solutions compared to GP-based approaches that often require repairing or penalising the solutions \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composition process is triggered by a composition goal defined in Subsection \ref{problemDes}, which describes customers requirements both semantic matchmaking quality and QoS. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 5. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is similar to \cite{da2016particle}, but we employ weighted graphs as a different solution presentation with explicit support for the proposed quality model.

\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
our PSO-based approach demands decoding processes from optimised queues to weighted DAGs, the bottlenecks of efficiently generating weighted DAGs lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted DAGs, we pre-calculate semantic matchmaking quality. The key idea of the index is to create a map using a pair of keys, output-related concepts and potentially matched input-related concepts with considering different levels of match types, and the map values stored $mt_{p}$ and $mt_{s}$. Meanwhile, this index size could also be reduced by only considering the concepts related in the shrunken service repository, which means the index cache is filtered by those task-relevant web services. This optimised cache also contributes to less and constant time for weighted graphs building through the whole evolutionary process.

@@

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; and $(2)$ compare solutions generated by a recent QoS-ware evaluation approach \cite{ma2015hybrid,da2016genetic} with our evaluation method proposed in the paper; and $(3)$ compare our PSP-based method with one existing GP-based approach \cite{ma2015hybrid}.

@@

The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations. We run 30 times independently for each dataset. We configure weight of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly. The $mt_{p}$ is set to 1 (Exact match) and 0.75 (Plugin). In general, weight settings and parameter match type quality are decided by users' preferences.

@@

\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
To evaluate the performance of our proposed PSO-based approach, we compare one GP-based approach  \cite{ma2015hybrid} with our PSO method. We consider the links between child nodes and parent nodes as semantic web service links for measuring  semantic matchmaking quality, and those links information are maintained correctly for the crossover and mutation. Therefore, we evaluate both semantic matchmaking quality and QoS simultaneously using the proposed comprehensive quality model. To make a fair comparison with our PSO-based, we consider the same number of evaluations (3000 times) as that in our PSO-based approach, we set the parameters settings for GP-based approach \cite{ma2015hybrid} using 30 individuals and 100 generations.
